Usage metrics

### 2020-12-19 analysis/usage.Rmd
Polish usage metrics

```{r}
lbl_colour <- rep("black", 11)
lbl_colour[[4]] <- "transparent"
E %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  stat_density(aes(y = ..count..), color = "black", fill = "blue", alpha = 0.3) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 10, 30, 100, 300, 1000), trans = "log1p", expand = c(0, 0)) +
  labs(x = "Size (AST nodes)") +
  theme(text = element_text(size=17),
        axis.text.x = element_text(color = lbl_colour))

E %>% 
  filter(ast_nodes < 25) %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  geom_histogram(binwidth = 1, color = "black", fill = "blue", alpha = 0.3) +
  scale_y_continuous(labels = comma)

@@

```{r}
E %>%
  filter(opcodes > 0) %>% # == 0 if from eval.parent, because we do not count eval loops for it
  filter(opcodes <= 50) %>%
  ggplot(aes(x = "", y = opcodes), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7, fill = "blue", alpha = 0.3) +
  labs(y = "Events", x = "") +
  theme(legend.position = "none", text = element_text(size=25))

>>>>

```{r}
lbl_colour <- rep("black", 11)
lbl_colour[[4]] <- "transparent"
E %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  stat_density(aes(y = ..count..), color = "black", fill = "blue", alpha = 0.3) +
  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5, 10, 30, 100, 300, 1000), trans = "log1p", expand = c(0, 0)) +
  labs(x = "Size (nodes)") +
  theme(text = element_text(size=17),
        axis.text.x = element_text(color = lbl_colour))

E %>% 
  filter(ast_nodes < 25) %>%
  ggplot(aes(x = ast_nodes, weight = duplicates)) +
  geom_histogram(binwidth = 1, color = "black", fill = "blue", alpha = 0.3) +
  scale_y_continuous(labels = comma) +
  labs(x = "nodes") +
  theme(text = element_text(size=17),  panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), aspect.ratio = 4/3)

@@

```{r}
E %>%
  filter(opcodes > 0) %>% # == 0 if from eval.parent, because we do not count eval loops for it
  filter(opcodes <= 50) %>%
  ggplot(aes(x = "", y = opcodes), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7, fill = "blue", alpha = 0.3) +
  labs(y = "Instructions", x = "") +
  theme(legend.position = "none", text = element_text(size=25))
